\newpage
\thispagestyle{plain}

{\centering\bf ABSTRACT\\}\par\vskip 2cm

\singleSpacing

\noindent
Hazra, Sudip %% last, first name, Title Case
M.Tech.  Department of Cyber Security Systems and Networks,
Amrita Vishwa Vidyapeetham,
2017.                           %% this year
{\sl Stealth File Systems for Proactive
Forensics Support in Custom Android
ROMs} %% title

\par\vskip 1cm

\doubleSpacing

Smartphones nowadays are capable of doing a multitude of tasks which was not possible
with conventional phones. The capabilities which makes smartphones different from con-
ventional phones is giving nightmares to security organisations in tracing and extracting
data from the smartphones. The criminals are now able to wipe out the traces of criminal ac-
tivities performed using their phones with much ease than before. The criminal organisations
are also using smartphones to communicate with others using encrypted messages which are
very hard to trace and decrypt. Even if the phones are confiscated after the crime, It is becoming very hard for law-enforcement agencies to extract data from those devices as these devices are encrypted with advanced encryption features and any attempt to get access to the device memory using brute-force would potentially wipe the all the data hence a proactive forensic framework was necessary for continuous monitoring of the criminals using their smartphones. The Proactive Forensic Rom is capable of monitoring the online and offline activities of the suspected criminals with high degree of precision and stealth while discretely uploading the user data to the cloud for further monitoring and analysis purpose.
\vfill

\noindent
{\bf Keywords:} Android, Forensics, Digital Evidence, Android
Framework, {\tt adb} tool, Pocket Spy.

\newpage




