\chapter{Mateti's {\LaTeX} Thesis Example}

I recommend that you use my collection of
files\footnote{\url{http://www.cs.wright.edu/~pmateti/Students/thesisExample.tbz}}.
My own contribution here is not original.  It is in pulling together
various needed pices in trying to reduce the \LaTeX-learning time for
my students.

\section{Contents of the {\tt tar} File}

The downloaded file is a {\tt tar} archive compressed with {\tt
  bzip2}.  You can untar it, in Linux, as in

{\tt tar xvfj thesisExample.tbz}

Your current directory will then have a new subdirectory called
ThesisEx/ with the following files and subdirectories in it.
[Ignore the dates, and usernames.]

\begin{verbatim}
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 13:07 Chapters/
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 11:44 Figures/
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 11:44 LaTeX/
-rw-r--r--    1 pmateti  pmateti       713 May 24 11:47 Makefile
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 13:09 Tables/
-rw-r--r--    1 pmateti  pmateti      8513 May 24 11:44 thesis.bib
-rw-r--r--    1 pmateti  pmateti      1158 May 24 11:47 thesis.tex
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 11:44 WSU/
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 11:44 AmritaU/
\end{verbatim}

\section{Your Use of these Files}

The files in the directory LaTeX are to be left as they are.  Note the
content of file named {\tt thesis.tex} from the very top to the line
\verb|\begin{document}|.  Edit these only if you are fluent in LaTeX.

Edit the files in the WSU or AmritaU directory to insert your own name,
etc.

Replace all the files in the {\tt Chapters/ Figures/ Tables/}
directories with yours.  Edit the {\tt thesis.tex} to input the files
in the {\tt Chapters/ Figures/ Tables/} directories.

Use the given {\tt Makefile} as a template and adjust.

This example template of a manuscript is written in the style of
learn-by-example.  The text body (in the pdf) shows what is possible,
and you are expected to study the \latex{} source of these chapters to
learn how things were done.

\section{Bib Files}
\label{BibFiles}

If you have several .bib files, move them into a {\tt BiB/} directory.
Note that \verb|\bibliography| does accept multiple filenames
(pathnames), separated by commas, but no spaces.  E.g., {\tt
  \verb|\bibliography|\{Bib/amrita, ..., Bib/cloud-comp,
  Bib/cloud-storage, Bib/code-audit, Bib/crowd-source, Bib/forensics,
  ..., Bib/malware, Bib/privacy, Bib/provenance,
  Bib/zygote-aslr-rop\}} is {\sc ok}.  Make sure there are no spaces,
and no ellipses -- I included these here just for readability.

% -eof-
